---
title: "Analysis of Canadian glaciers"
author: "Anastasiia Vynychenko"
date: "20 February 2019"
output:
  pdf_document: 
    toc: TRUE
  html_document: 
    toc: TRUE
    toc_float: TRUE
urlcolor: blue
params:
  filename: "https://raw.githubusercontent.com/tonytonov/Rcourse/master/R%20markdown/demos/glacier.csv"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
```

### Introduction

The data for analysis was  taken from the: <http://open.canada.ca/data> [^1]

[^1]: [Direct link for downloading file](https://raw.githubusercontent.com/tonytonov/Rcourse/master/R%20markdown/demos/glacier.csv)

### Short Summary

```{r chunk1}
glacier <- read.csv(params$filename, comment.char = "#", na.strings = "..")
```

Through all glaciers <u>the shortest history</u> of observations has: *`r sel <- glacier %>% 
  group_by(GEO) %>% 
  summarise(Date = max(Ref_Date) - min(Ref_Date)) %>% 
  arrange(Date) %>% 
  slice(1) %>% 
  select(GEO)
sel[[1]]`*

Also, the glacier, which has <u>median value of changes the most close to zero</u>, calls: *`r selection <- glacier %>% 
  group_by(GEO, MEASURE) %>% 
  filter(MEASURE == "Annual mass balance") %>% 
  summarise(Median = median(Value, na.rm = T)) %>% 
  arrange(-Median) %>%
  select(GEO)
selection[[1]][1]`*


<u>The only</u> missing value of observation has history of the glacier calls 
*`r glacier$GEO[is.na(glacier$Value)]`*





