---
title: "Analysis of annual incomes and spending capacity depending on gender"
author: "Anastasiia Vynychenko"
date: '22 April 2019'
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
  pdf_document:
    toc: TRUE
params:
  file: "https://raw.githubusercontent.com/avynychenko/R_studing_tasks/master/Data%20for%20tasks/Mall_Customers.csv"
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(ggplot2)
library(plotly)
```

### Intro

The main purpose of this analysis is to understand if there is some connections between "spending money capacity" and gender.
For resolving this issue, data was taken from resource: <https://www.kaggle.com/> [^1]

[^1]:[Direct link for downloading file](https://www.kaggle.com/vjchoudhary7/customer-segmentation-tutorial-in-python)

Here you can see how the header of data looks like:
```{r read}
data <- read.csv(params$file)
new_data <- data %>% 
  rename(annual_income = Annual.Income..k..,
         spending_score = Spending.Score..1.100.)
head(new_data)
```

### Analyzing part

#### Correlation between gender and annual income

Let's take a look to our data set. First of all, we want to understand quantity of Female & Male in our data and how age in each group is distributed.

Here is summary of data:

```{r summary}
new_data %>% 
  group_by(Gender) %>% 
  summarise(quantity = n(),
            max_age = max(Age),
            mean_age = mean(Age),
            min_age = min(Age),
            mean_income = mean(annual_income)
            )
```

From this tibble we can see that all indicators are almost equal. We also can see that mean age in male and female groups also equal, the same situation with income, etc. Only a small difference in quantity of participants, but it's no so huge. That's why we can carry on with our analysis.
Despite the fact that we saw the summary table, it's better to visualize our data.

```{r}
ggplotly(ggplot(new_data, aes(Age, annual_income, col = Gender)) +
  geom_point(size = 2) + 
  scale_y_continuous(name = "Annual income per year") +
  theme_bw() +
  scale_color_brewer(type = "qual", palette = 6 ))
```

From this graph we can see that in our data there is no correlation between income and age that people gained per year. Also there is no difference in both groupes: male and female.

Finally let's try to prove this hypotesis with **ANOVA analysis**.

```{r}
summary(aov(annual_income ~ Gender, new_data))
```

We received P-value = 0.428 that tell us that we can accept this hypotesis, telling us that people in two groups (Female and Male) don't have differences in their incomes.

#### Clusterizing

The next step, which help us to understand our data better is to split customers to different groups, which will be different, in comparison with Gender characteristics.

First of all we should choose what amounts of clusters we want to pick out. Let's do this with hierarchical clusterization. 

Consider this graph:

```{r}
data <- new_data[sapply(new_data, is.numeric)]
fit <- hclust(dist(data))
plot(fit)
rect.hclust(fit, 5) 
```

Analyzing this graph, it will be optimally to choose 5 clusters. 
Let's assign all customers to specific cluster and we will do this, using K-Means Model.
Before clustering, I will normalize data, using Z-score method.
```{r warning=FALSE}
norm_data <- as.data.frame(lapply(new_data, function(x) if (is.numeric(x) & x != data[[1]]) scale(x) else x))
clusters <- kmeans(norm_data[,4:5], 5, nstart = 30)
norm_data$cluster <- as.factor(clusters$cluster)
head(norm_data)
```

Here we can see the beggining of table with normalized numeric variables and assigned number of cluster.

#### Analyzing of spending money

Well, now we can look at graph and see what behaviour of "spending money capacity" for all 5 subgroups of customers.

```{r}
ggplotly(ggplot(norm_data, aes(annual_income, spending_score, col = cluster)) +
  geom_point() +
  scale_y_discrete(name = "Spending score") +
  scale_x_continuous(name = "Income per year") +
  facet_wrap(~Gender) +
  theme_bw() +
  scale_color_brewer(type = "qual", palette = 6 ))
```

Here we can see no difference in behaviour of spending money eather it female or male. 
We only can see difference depending on cluster, which we assigned to each customer.

### Conclusion

So, in conclusion we can claim:

1. There is no difference in "spending money capacity" between genders.
2.  There is an existing difference in "spending money capacity", depending on subgroups (clusters), which we can assign based on annual incomes and spending score.


